---
title: "week 2 test"
author: "ashy"
date: "10 November 2017"
output: html_document
---
=============================================

## Week 2 test
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Loading the data set
We have many NA's in out "steps" column
```{r}
Week2 <- read.csv("C:\\Ashy\\Ashy\\cousera\\Reproducible research\\week 2\\activity.csv")

summary(Week2)

table(is.na(Week2$steps))

str(Week2)
```

What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

Calculate the total number of steps taken per day
#Week2$steps[is.na(Week2$steps)]  <- 0 #replacing the NA's with Zero

```{r total number of steps per day}

steps <- aggregate(Week2$steps, by = list(Date = Week2$date), FUN = sum)

names(steps)[names(steps) == "x"] <- "Total"
temp <- as.Date(steps$Date, "%Y-%m-%d")
steps$Date <- format(temp, format = "%m-%d")
head(steps)



```

Make a histogram of the total number of steps taken each day.

```{r}
with(steps,hist(Total))

```


Calculate and report the mean and median of the total number of steps taken per day
```{r mean}
mean(steps$Total,na.rm = TRUE)


median(steps$Total,na.rm = TRUE)

```

What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}

library(ggplot2)

Five_Min <- aggregate(steps ~ interval, data = Week2, FUN =mean)

TimeSeries <- ggplot(data = Five_Min, aes(x = interval, y = steps)) + 
    geom_line() +
    xlab("Time Intervals") + 
    ylab("Total Number of Steps") +
    ggtitle("Avg. steps")

print(TimeSeries)


```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
Five_Min[which(Five_Min$steps == max(Five_Min$steps)),]

```


Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
table(is.na(Week2)) #2304 nulls
sapply(X = Week2, FUN = function(x) sum(is.na(x)))

```

Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc

Create a new dataset that is equal to the original dataset but with the missing data filled in

```{r}
names(Five_Min)[2] <- "mean.steps"

New <- merge(Week2, Five_Min)
New$steps[is.na(New$steps)] <- New$mean.steps[is.na(New$steps)]

```

Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}
#creating a dta set with the number of steps per day.
library(dplyr)
day.imp <- group_by(New, date)
day.imp <- summarize(day.imp, steps=sum(steps))
#histogram showimg the summary statistics
qplot(steps, data=day.imp)
```

Are there differences in activity patterns between weekdays and weekends?

For this part the weekdays() function may be of some help here. Use the dataset with the filled-in missing values for this part.

Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
```{r}

#First I create separate data frames for weekends and weekdays:
New$dayofweek <- weekdays(as.Date(New$date))
New$weekend <-as.factor(New$dayofweek=="Saturday"|New$dayofweek=="Sunday")
levels(New$weekend) <- c("Weekday", "Weekend")

weekday <- New[New$weekend=="Weekday",]
weekend <- New[New$weekend=="Weekend",]

#Then for each one, I find the mean number of steps across days for each 5 minute interval:
weekday <- group_by(weekday, interval)
weekday <- summarize(weekday, steps=mean(steps))
weekday$weekend <- "Weekday"
weekend <- group_by(weekend, interval)
weekend <- summarize(weekend, steps=mean(steps))
weekend$weekend <- "Weekend"

#
final <- rbind(weekday, weekend)
final$weekend <- as.factor(final$weekend)
ggplot(final, aes(interval, steps)) + geom_line() + facet_grid(weekend ~ .)
```


```{R}


```